TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
minor

In the following, properties are defined in the context of a
search tree $\mathfrak{T}$. In Definition~\ref{def:solved}, we specify
different status for a goal: open, pending or solved. There, we define
what a solved goal and solved node are by mutual recursion on the number of
steps it takes to solve a goal and a node.
\begin{definition}\label{def:solved}(Solved goal, solved nodes, open goal,
pending goal)\\
The set of solved nodes $\mathbb{A}^\infty$ and
the set of solved goals $\mathbb{G}^\infty$ are defined inductively by:

@@

We call a goal (respectively node) unsolved if it is not in the set of solved
goal (respectively node).
The open goal of a node is the first unsolved goal of this node according to
some preset order. The other unsolved nodes are called pending nodes.
If a node is unsolved, then it contains a unique open goal.
During MCTS exploration, we do not explore pending goals of an unsolved node
before its open goal is solved which justifies our terminology. In other words,
our search tree has the following property: if $g$ is a pending node then
$T(g)$ is empty.

>>>>

In the following, properties are defined in the context of a
search tree $\mathfrak{T}$. In Definition~\ref{def:solved}, we specify
different status for a goal: open, pending or solved. There, we define
what a solved goal and solved node are by mutual recursion on the number of
steps it takes to solve a goal and a node.
\begin{definition}\label{def:solved}(solved goal, solved nodes, open goal,
pending goal)\\
The set of solved nodes $\mathbb{A}^\infty$ and
the set of solved goals $\mathbb{G}^\infty$ are defined inductively by:

@@

We call a goal (respectively node) unsolved if it is not in the set of solved
goals (respectively nodes).
The open goal of a node is the first unsolved goal of this node according to
some preset order. The other unsolved nodes are called pending nodes.
If a node is unsolved, then it contains a unique open goal.
During MCTS exploration, we do not explore pending goals of an unsolved node
before its open goal is solved which justifies our terminology. In other words,
our search tree has the following property: if $g$ is a pending node then
$T(g)$ is empty.
